\documentclass[10pt]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{fontspec}

\usepackage[margin=1.15in]{geometry}
\usepackage{setspace, titling}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

%% FONTS
\usepackage{fontspec}
% See: https://tex.stackexchange.com/a/50593
\setmainfont[
BoldFont       = FiraSans-SemiBold.otf,
ItalicFont     = FiraSans-Italic.otf,
BoldItalicFont = FiraSans-SemiBoldItalic.otf
]{FiraSans-Regular.otf} %
\setmonofont[
BoldFont       = FiraCode-Bold.ttf
]{FiraCode-Regular.ttf}
\usepackage{marvosym} % For cool symbols.
\usepackage{fontawesome} % Ditto

\usepackage[normalem]{ulem} %% For strikeout font: \sout()

\usepackage[dvipsnames]{xcolor}
\definecolor{uo_green}{HTML}{154733}
\definecolor{forest_green}{HTML}{006241}
\definecolor{pine_green}{HTML}{007935}
\definecolor{grass_green}{HTML}{62A70F}
\definecolor{golden_yellow}{HTML}{FFD200}
\definecolor{cool_gray}{HTML}{54565B}
\definecolor{light_cool_gray}{HTML}{A8A8AA}

\usepackage[colorlinks = true,
linkcolor = pine_green,
urlcolor  = pine_green,
citecolor = pine_green,
anchorcolor = black]{hyperref}
\usepackage{graphicx}

% For table formatting:
\usepackage{array, booktabs, caption, siunitx}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}

\begin{document}

\title{
	\texttt{\textbf{Introduction to Econometrics} [EC425/525]}\\[1em]
	\large Spring 2019 Syllabus
}
\author{Dr. Edward Rubin\\ Dept. of Economics, University of Oregon}
%\date{}  % Toggle commenting to test
\date{\vspace{-5ex}}

\maketitle

\section*{Basics}

\begin{table}[!h]
	\ra{1.2}
\begin{tabular}{@{\extracolsep{5pt}} l l l l l l @{}}
	& \underline{\textbf{{Lecture}}} & \underline{\textbf{{Lab}}} & \underline{\textbf{{Office Hours}}} \\
	\faClockO & Mo. \& We., 1000--1120 & Fr. 12--1250 & Mo., 1600--1700; Th., 0900-1000 \\
	\faMapMarker & \href{https://map.uoregon.edu/c721c7d95}{McKenzie 240A} & \href{https://map.uoregon.edu/e5567cb0a}{Gerlinger 302} & \href{https://map.uoregon.edu/e6bd451c7}{PLC 519} \\
	\faUser & Edward Rubin & - & Edward Rubin \\
  \faBook & \multicolumn{5}{l}{\href{http://smile.amazon.com/Introduction-Econometrics-Christopher-Dougherty/dp/0199676828/}{Introduction to Econometrics, 5\textsuperscript{th} ed. }} \\
  \faBook & \multicolumn{5}{l}{\href{https://www.amazon.com/Mastering-Metrics-Path-Cause-Effect/dp/0691152845/}{Mastering `Metrics: The Path from Cause to Effect}}
\end{tabular}
\end{table}

\begin{table}[!h]
	% \centering
	\ra{1.2}
\begin{tabular}{@{\extracolsep{5pt}} ll @{}}
	& \underline{\textbf{{Contact}}}\\
	\faUser & Edward Rubin\\
	\faPaperPlaneO & \href{mailto:edwardr@uoregon.edu}{edwardr@uoregon.edu}\\
	 & Use ``\texttt{EC525}'' in email subject.\\
	\faTwitter & \href{https://twitter.com/search?src=typd&q=%23ec525}{\#ec525}\\
	\faChevronRight & \href{https://github.com/edrubin/EC525W19}{https://github.com/edrubin/EC525W19} \\
  & Our course on Github \\
  \faChevronRight & \href{https://edrub.in}{https://edrub.in}\\
\end{tabular}
\end{table}

\section*{Cellphone policy}

\textbf{No phones.} You cannot use your phone in class---texting included. Offenders will lose 1 percentage point off of their final grade for each offense. If you have a concern about this policy, please contact me via email or discuss in office hours during the first week of classes.

\bigskip \noindent The only exceptions to this rule:
\begin{enumerate}
  \item An emergency.
  \item Activities in class \textit{in which I ask you to use your phone}.
\end{enumerate}

\section*{Course summary}

\paragraph{Description:} This course aims to prepare economics majors for the demands of real-world applications. Toward this goal, we will examine the assumptions that underly the econometric and statistical models that you learned in Economics 320 (along with Math 243). These models imposed strong assumptions that are often violated in practice. Thus, we will relax these assumptions---replacing them with looser, more palatable assumptions---and derive, build, and estimate the resulting new models. By the end of this course, students should have the ability to statistically examine the bulk of economic issues using econometrics---knowing how to empirically test economic models and knowing the strengths, weaknesses, and assumptions of their chosen route of analysis.

Learning statistical programming is inherent to practicing applied econometrics. Consequently, throughout this course we will also teach the statistical programming language \texttt{{R}}.

\paragraph{Prerequisites:} This course requires Economics 423/523 and 424/525.

\section*{Software and tools}

\begin{itemize}
  \item We will use the statistical programming language \href{https://www.r-project.org/}{\textbf{\texttt{R}}}.
  \item We will use \href{https://www.rstudio.com}{\textbf{\texttt{RStudio}}} to interact with \texttt{R}.
\end{itemize}
Learning \texttt{R} will require time and effort, but it is a powerful and versatile tool that is valued by many employers. Put in the requisite effort and time, and you will be rewarded. \textbf{Step 1:} Install \texttt{R} and \texttt{RStudio} on your own computer.

If you are concerned about learning \texttt{R}---or want to learn more/quickly---I suggest that you check out the following free, online resources.
\begin{itemize}
  \item \href{https://www.datacamp.com/courses/free-introduction-to-r}{DataCamp's \textit{Introduction to R}}
  \href{https://www.teamleada.com/courses/r-bootcamp}{TeamLeada's \textit{R Bootcamp}}
  \item \href{https://www.computerworld.com/article/2497143/business-intelligence-beginner-s-guide-to-r-introduction.html}{Computerworld's \textit{Beginner's guide to R}}
\end{itemize}
The folks at \texttt{RStudio} put together a  \href{https://www.rstudio.com/online-learning/}{set of resources} (I found the two resources above on their list).

\section*{Labs, homework, and exams}

\paragraph{Lab:} This course includes a lab, which is integral to learning the material in this course. The lab includes general econometrics instruction but will focus on computing tips necessary to complete the homework assignments---linking the lecture material to \texttt{R}.

\paragraph{Problem Sets}
\begin{itemize}
  \item You will \textbf{turn in assignments online via Canvas}.
  \item Assignments will be due approximately every other week.
  \item See below for \textbf{late policy}.
\end{itemize}
Feel free to work together on the assignments. Unless explicitly stated, \textbf{each student is required to write and submit independent answers}. This means that word-for-word copies will not be accepted and will be viewed as academic dishonesty. If you work with other students, you must list the students in your study group at the top of your assignment. If you fail to do so, you will receive a score of zero.

We will accept assignments \textbf{up to 48 hours late}, but we will \textbf{subtract 2 percentage points for each hour it is late.} For example, you turn in an assignment 12 hours late and would have received 85\%. We subtract 12$\times$2$=$24 percentage points, meaning you will receive 85\%$-$24\%=61\%.

\paragraph{Exams}
\begin{itemize}
  \item We will proctor the \textbf{in-class midterm on February 12, 2019} in \href{https://map.uoregon.edu/c721c7d95}{McKenzie Hall 240A}.
  \item We will proctor the \textbf{final exam on March 18, 2019 from 12:30pm--2:30pm} (location TBA).
\end{itemize}
If you will be out of town for these exams, you must take the exam at a testing center at a university in whichever town you will be visiting at the same time as the EC525 scheduled exam (or take a zero).

\section*{Grades}

Grades for this class will be assigned based on the following assignments: biweekly homework assignments, one midterm exam, and one final exam. Final grades will be determined based on your rank-ordered position within the class. You can
track your grades for individual assignments on Canvas. The weights for the final grade:
\begin{table}[!h]
  \ra{1.2}
  \centering
  \begin{tabular}{@{\extracolsep{2cm}}ll@{}}
    \textbf{Problem Sets} & 35\% \\
    \textbf{Midterm}      & 30\% \\
    \textbf{Final Exam}   & 35\%
  \end{tabular}
\end{table}
While attendance is voluntary---both for lecture and for lab---we will occasionally have in-class and in-lab quizzes, problems, or opportunities for extra credit. These exercises will go into your \textit{Problem Sets} grade.

\section*{Textbook and other readings}

One of the goals of this course is to make you aware of the incredible array of instruction material that is freely available online. I also want to encourage you to be entrepreneurial (key for learning to program).

\paragraph{Econometrics books:} There are two recommended textbooks for this course.

\begin{enumerate}
  \item \href{https://www.amazon.com/Mastering-Metrics-Path-Cause-Effect/dp/0691152845/}{\textbf{Mastering `Metrics: The Path from Cause to Effect}} by Angrist and Pischke (\textbf{MM})
  \item \href{http://smile.amazon.com/Introduction-Econometrics-Christopher-Dougherty/dp/0199676828/}{\textbf{Introduction to Econometrics}, 5\textsuperscript{th} ed.} by Christopher Dougherty (\textbf{ItE})
\end{enumerate}
You can purchase these books at the UO Duckstore (you should already have ItE from EC320). I strongly recommend that you read the assigned readings from the textbooks. Attending class is not a replacement for reading and comprehending the texts---nor will solely reading sufficiently replace class. The course schedule (farther below) contains suggested readings for each topic.

\paragraph{R books:} For learning \texttt{R}, I recommend Garrett Grolemund and Hadley Wickham's \href{http://r4ds.had.co.nz}{\textbf{\textit{R} for Data Science}}, which is available for free online. Want to go deeper? Check out \href{http://adv-r.had.co.nz/}{\textbf{Advanced \textit{R}}} (Hadley Wickham, again) and \href{http://socviz.co/}{\textbf{Data Visualization: A practical introduction}} (Kieran Healy)---both books are free online.

\newpage

\section*{Lab GE contact information}
\begin{table}[!h]
  \centering
  \ra{1.1}
  \begin{tabular}{@{\extracolsep{2cm}} l l @{}}
    \textbf{Tuesday Labs:} & \textbf{Thursday Labs:}  \\
    John Morehouse & Alex Li \\
    Office: PLC 508 & Office: PLC 508 \\
    Email: jmorehou@uoregon.edu & Email: jungangl@uoregon.edu \\
    Office hours: Mo., 1630--1730 & Office hours: We., 1630--1730 \\
  \end{tabular}
\end{table}

\noindent \textbf{Note:} Feel free to go to any office hours. Don't feel restricted to only go to those of your lab GE.

\section*{Honesty and academic integrity}

You must do your own work. Do not claim credit for any work other than your own. Cheating or plagiarizing of any sort on any component of this class will result in a failing grade for the term and a report of the offense to the university. Please acquaint yourself with the \href{http://studentlife.uoregon.edu}{Student Conduct Code}.

\section*{Accessibility}

If you have a documented disability and anticipate needing accommodations in this course, please make arrangements with me during the first week of the term. Please request that the \href{https://aec.uoregon.edu/}{Accessible Education Center} send me a letter verifying your disability.

\section*{Tentative course outline}

The next page presents the current plan for the course outline and associated textbook reading assignments. We will occasionally assign papers for you to read for class, lab, or your homework assignments. I will post these papers on Canvas. As the title of this section suggests, the timing and topics on this schedule may change.

\begin{table}[htb]
  \caption*{\textbf{Tentative course schedule}}
  \ra{1.5}
  \begin{tabular}{@{\extracolsep{1cm}} c c l l @{}}
    \toprule
    \textbf{Class} & \textbf{Date} & \textbf{Topics} & \textbf{Suggested readings}  \\ \toprule
    \texttt{01} & 04/01 & Introduction \& Review & ItE 1--6 \\
    \texttt{02} & 04/03 & Review & ItE 1--6; MM 2 \\
    \texttt{03} & 04/08 & Review & ItE 1--6; MM 2 \\
    \texttt{04} & 04/10 & Heteroskedasticity & ItE 7 \\
    \texttt{05} & 04/15 & Heteroskedasticity & ItE 7 \\
    \texttt{06} & 04/17 & Consistency (and Inconsistency) & ItE pp. 68--75  \\
    \texttt{07} & 04/22 & TBA & TBA \\
    \texttt{08} & 04/24 & Time Series & ItE 11  \\
    \texttt{09} & 04/29 & Time Series & ItE 11  \\
    \texttt{10} & 05/01 & Midterm Review & ItE 12 \\ \midrule
    \texttt{11} & 05/06 & \textbf{In-Class Midterm} \\ \midrule
    \texttt{12} & 05/08 & Autocorrelation & ItE 12 \\
    \texttt{13} & 05/13 & Autocorrelation \& Nonstationarity & ItE 12 \& 13 \\
    \texttt{14} & 05/15 & Causality & MM 1 \\
    \texttt{15} & 05/20 & Instrumental Variables & ItE 9; MM 3 \\
    \texttt{16} & 05/22 & Instrumental Variables & ItE 9; MM 3 \\
    \texttt{17} & 05/27 & Panel Data Methods & ItE 14; MM 5 \\
    \texttt{18} & 05/29 & Panel Data Methods & ItE 14; MM 5 \\
    \texttt{19} & 06/03 & Difference in differences & MM 5 \\
    \texttt{20} & 06/05 & Additional topics & TBA \\ \midrule
    \texttt{  } & 06/12 & \textbf{Final Exam, 10:15 am} & \\
    \bottomrule
  \end{tabular}
\end{table}


\end{document}
